Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/fig-motivation.tex
right-align numbers
footnote moved

\begin{figure*}
\centering
\begin{tabular}{llll}
\toprule
 \bf Classification & \bf Example CVE & \bf Example description & \bf Count\\
\midrule
  Memory corruption\footnote{We classified the following vulnerabilities as memory corruption
    attacks based on their description: 2013-5660, - 0742, -0138, 2012-4987, -1163,-1162, 2011-2265,
    2010-4535, -1657, -1336, -1218} & 2013-5660 & Buffer overflow & 11\\
  Parser ambiguities & 2013-1462 & Multiple virus scanners interpret ZIP files incorrectly.& 4\\
  Semantic misunderstanding & 2014-2319 & Weak cryptography used even if user selects AES & 1\\
  \multicolumn{3}{l}{\bf Total vulnerabilities related to .zip processing }& \bf 16  \\
\bottomrule

>>>>

\begin{figure*}
\centering
\begin{tabular}{lllr}
\toprule
 \bf Classification & \bf Example CVE & \bf Example description & \bf Count\\
\midrule
  Memory corruption & 2013-5660 & Buffer overflow & 11\\
  Parser ambiguities & 2013-1462 & Multiple virus scanners interpret ZIP files incorrectly.& 4\\
  Semantic misunderstanding & 2014-2319 & Weak cryptography used even if user selects AES & 1\\
  \multicolumn{3}{l}{\bf Total vulnerabilities related to .zip processing }& \bf 16  \\
\bottomrule

### 2014-05-02 paper/osdi14/motivation.tex
footnote moved

These input processing vulnerabilities fall into two broad classes.  The first
class, which occurred 11 times, is memory safety bugs, such as buffer overflows, which allow an
adversary to corrupt the application's memory using specially crafted
inputs.  These mistakes arise in lower-level languages that do not
provide memory safety guarantees, such as C, and can be partially
mitigated by a wide range of techniques, for example static analysis,
dynamic instrumentation, and address space layout randomization, that
make it more difficult for an adversary to exploit these bugs.
Nail helps developers using lower-level languages to avoid these bugs
in the first place.

>>>>

These input processing vulnerabilities fall into two broad classes.  The first
class, which occurred 11 times\footnote{We classified the following vulnerabilities as memory corruption
    attacks based on their description: 2013-5660, - 0742, -0138, 2012-4987, -1163,-1162, 2011-2265,
    2010-4535, -1657, -1336, -1218}, is memory safety bugs, such as buffer overflows, which allow an
adversary to corrupt the application's memory using specially crafted
inputs.  These mistakes arise in lower-level languages that do not
provide memory safety guarantees, such as C, and can be partially
mitigated by a wide range of techniques, for example static analysis,
dynamic instrumentation, and address space layout randomization, that
make it more difficult for an adversary to exploit these bugs.
Nail helps developers using lower-level languages to avoid these bugs
in the first place.
